---
title: "vignettes"
output: rmarkdown::html_vignette
# output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MasteringSofwareDevelopmentInRCapstone)
library(dplyr)
library(lubridate)
library(stringr)
library(ggplot2)
library(tidyr)
library(leaflet)
```

First of all, lets clean the data-raw (direct download from NOAA):

```{r}
df <- eq_clean_data(NOAArawData='../data-raw/earthquakes-2021-10-06_09-24-38_+0200.tsv')
head(df)
```

Apply correction to the location and create the attributes: COUNTRY and LOCATION_NAME. Also store the data as a default dataset in the library
```{r}
dfclean <- eq_location_clean(df)

# store in data
# use_data(dfclean)
```

With the clean data lest see a plot of CHINA AND GREECE between 2015 and 2021...
```{r}
dfs <- dfclean %>%
  dplyr::filter(Year>2015 & Year<2021 & (COUNTRY =='CHINA' | COUNTRY =='GREECE'))

p1 <- dfs %>%
ggplot() +
geom_timeline(aes(x = Date,
                  y = COUNTRY,
                  size = Mag,
                  colour = Deaths)) +
  theme_minimal()+
  theme(legend.position="bottom")

p1
```

Add now the LOCATION_NAME  to the plot...
```{r}
p2 <- p1 + geom_eqloc(aes(x = Date, y = COUNTRY, locations = LOCATION_NAME, number = 3))
p2
```

Lest plot the map with the previous selected points
```{r}
p3 <- dfs %>% eq_map(annot_col = "Date")
p3
```


Finally, lets change the popup style within the map points:
```{r}
dfs %>%
  mutate(popup = eq_create_label(.)) %>%
  eq_map(annot_col = "popup")
```

